---
title: "pa_phone_sensedoc"
author: "Daniel Fuller"
date: "23/02/2021"
output:
  html_document: 
    keep_md: yes
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Required packages
```{r}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(naniar)
library(ggmap)
library(ggthemes)
library(sf)
library(rgeos)
library(cancensus)
library(cowplot)
library(ggspatial)
library(knitr)

setwd("/Users/dfuller/Dropbox/Projects/INTERACT_github/pa_phone_sensedoc/")
```

# Physical Activity

https://reader.elsevier.com/reader/sd/pii/S1440244011000788?token=EF8BC1F1D26E1549EB101EBB8B8F90E8A13690C5BBCE4B0E263DE65441B5D61D63D1E3CD243FE9138D314E9E6E13DB28

### Reading in the physical activity data from SenseDoc
```{r warning=FALSE}
data_temp <- NULL

data_temp <- dir(path = "/Users/dfuller/Documents/INTERACT/data/sensors/", full.names = TRUE, pattern = "*_sd.csv", recursive = TRUE) %>%
   purrr::map(function(i){
     dfhx <- read.csv(i, header = TRUE)
     temp <- bind_rows(data_temp, dfhx)
   })

sd_data <- bind_rows(data_temp)
rm(data_temp)
table(sd_data$city)
```

### Reading in the physical activity data from Ethica
```{r warning=FALSE}
data_temp <- NULL

data_temp <- dir(path = "/Users/dfuller/Documents/INTERACT/data/sensors/", full.names = TRUE, pattern = "*_ethica.csv", recursive = TRUE) %>%
   purrr::map(function(i){
     dfhx <- read.csv(i, header = TRUE)
     temp <- bind_rows(data_temp, dfhx)
   })

ethica_data <- bind_rows(data_temp)
rm(data_temp)
table(ethica_data$city)
```

## Some basic cleaning

```{r warning=FALSE}
sd_data <- sd_data %>% filter(wearing == 1)
ethica_data <- ethica_data %>% filter(wearing == 1)
```

## Applying Cut-points from this paper (using 3 axes VM)

https://www.sciencedirect.com/science/article/pii/S1440244011000788

    Light: 0 - 2690 CPM 
    Moderate: 2691 - 6166 CPM
    Vigorous: 6167 - 9642 CPM
    Very Vigorous: 9643 - ∞ CPM

```{r warning=FALSE}
sd_data <- sd_data %>%
	mutate(activity_levels_vm3 = case_when(
		summary_count <= 2690 ~ "light",
		summary_count >= 2691 & summary_count <= 6166 ~ "moderate",
	  summary_count >= 6167 ~ "vigorous"
	))

ethica_data <- ethica_data %>%
	mutate(activity_levels_vm3 = case_when(
		summary_count <= 2690 ~ "light",
		summary_count >= 2691 & summary_count <= 6166 ~ "moderate",
	  summary_count >= 6167 ~ "vigorous"
	))
```

### Troiano cut-points on vertical axis counts

```{r}
sd_data <- sd_data %>%
	mutate(activity_levels = case_when(
		x_count < 100 ~ "sedentary",
		x_count >= 100 & x_count <= 1951 ~ "light",
		x_count >= 1951 & x_count <= 5724 ~ "moderate",
	  x_count >= 5725 ~ "vigorous"
	))

ethica_data <- ethica_data %>%
	mutate(activity_levels = case_when(
		x_count < 100 ~ "sedentary",
		x_count >= 100 & x_count <= 1951 ~ "light",
		x_count >= 1951 & x_count <= 5724 ~ "moderate",
	  x_count >= 5725 ~ "vigorous"
	))
```

## Create a date column and add a minutes in census tract by id, date, and census tract column 

```{r}
#### SenseDoc
sd_data$date <- sd_data$utcdate %>% as.Date()
sd_data$minutes <- 1

sd_data <- sd_data %>% 
  group_by(interact_id, date, city_id) %>% 
  mutate(
      minutes_id_date_city = sum(minutes)
  )

### Ethica
ethica_data$date <- ethica_data$utcdate %>% as.Date()
ethica_data$minutes <- 1

ethica_data <- ethica_data %>% 
  group_by(interact_id, date, city_id) %>% 
  mutate(
      minutes_id_date_city = sum(minutes)
  )
```

### MPVA Minutes SenseDoc

```{r}
table(sd_data$activity_levels)

table(sd_data$wearing)

### MVPA Minutes
sd_data <- sd_data %>%
	mutate(mvpa_vm3 = case_when(
		activity_levels_vm3 == "light" ~ 0,
		activity_levels_vm3 == "moderate" ~ 1,
		activity_levels_vm3 == "vigorous" ~ 1
	))

table(sd_data$mvpa_vm3)

### Light Minutes
sd_data <- sd_data %>%
	mutate(light_vm3 = case_when(
		activity_levels_vm3 == "light" ~ 1,
		activity_levels_vm3 == "moderate" ~ 0,
		activity_levels_vm3 == "vigorous" ~ 0
	))

sd_data <- sd_data %>% 
    group_by(interact_id, date, city_id) %>% 
      mutate(
        total_mvpa_minutes = sum(mvpa_vm3),
        total_light_pa_minutes = sum(light_vm3)
        )

sd_pa_table <- sd_data %>%
                group_by(interact_id, date, city_id) %>%
                  summarize(
                    time = mean(minutes_id_date_city, na.rm = TRUE),
                    wearing = mean(wearing, na.rm = TRUE),
                    mean_mvpa_sd = mean(total_mvpa_minutes, na.rm = TRUE), 
                    mean_light_sd = mean(total_light_pa_minutes, na.rm = TRUE), 
                    na_count = sum(is.na(total_mvpa_minutes)), 
                    count = n()
                  )
sd_pa_table

sd_sum_table <- sd_pa_table %>%
                group_by(city_id) %>%
                  summarize(
                    time = mean(time, na.rm = TRUE), 
                    wearing = mean(wearing, na.rm = TRUE), 
                    mean_mvpa_sd = mean(mean_mvpa_sd, na.rm = TRUE), 
                    mean_light_sd = mean(mean_light_sd, na.rm = TRUE), 
                    na_count = sum(is.na(time)), 
                    count = n()
                  )
sd_sum_table
```

### MPVA Minutes Ethica

```{r}
table(ethica_data$activity_levels)

table(ethica_data$wearing)

### MVPA Minutes
ethica_data <- ethica_data %>%
	mutate(mvpa_vm3 = case_when(
		activity_levels_vm3 == "light" ~ 0,
		activity_levels_vm3 == "moderate" ~ 1,
		activity_levels_vm3 == "vigorous" ~ 1
	))

table(ethica_data$mvpa_vm3)

### Light Minutes
ethica_data <- ethica_data %>%
	mutate(light_vm3 = case_when(
		activity_levels_vm3 == "light" ~ 1,
		activity_levels_vm3 == "moderate" ~ 0,
		activity_levels_vm3 == "vigorous" ~ 0
	))

ethica_data <- ethica_data %>% 
    group_by(interact_id, date, city_id) %>% 
      mutate(
        total_mvpa_minutes = sum(mvpa_vm3),
        total_light_pa_minutes = sum(light_vm3)
        )

eth_pa_table <- ethica_data %>%
                group_by(interact_id, date, city_id) %>%
                  summarize(
                    time = mean(minutes_id_date_city, na.rm = TRUE),
                    wearing = mean(wearing, na.rm = TRUE),
                    mean_mvpa_sd = mean(total_mvpa_minutes, na.rm = TRUE), 
                    mean_light_sd = mean(total_light_pa_minutes, na.rm = TRUE), 
                    na_count = sum(is.na(total_mvpa_minutes)), 
                    count = n()
                  )
eth_pa_table

eth_sum_table <- eth_pa_table %>%
                group_by(city_id) %>%
                  summarize(
                    time = mean(time, na.rm = TRUE), 
                    wearing = mean(wearing, na.rm = TRUE), 
                    mean_mvpa_sd = mean(mean_mvpa_sd, na.rm = TRUE), 
                    mean_light_sd = mean(mean_light_sd, na.rm = TRUE), 
                    na_count = sum(is.na(time)), 
                    count = n()
                  )
eth_sum_table
```

### Joining SenseDoc and Ethica

```{r}
sd_eth <- inner_join(sd_data, ethica_data, by = c("interact_id", "utcdate"))

summary(sd_eth$summary_count.x)

summary(sd_eth$summary_count.y)

cor.test(sd_eth$summary_count.x, sd_eth$summary_count.y)
```

### Cross tab between VM3 cut points 

```{r}
table(sd_eth$activity_levels_vm3.x, sd_eth$activity_levels_vm3.y)
```

### Cross tab between vertial axis cut points 

```{r}
table(sd_eth$activity_levels.x, sd_eth$activity_levels.y)
```

### Regressing Sensedoc vertical axis count categories on Ethica data VM3 data

```{r}
glimpse(sd_eth$activity_levels.x)
sd_eth$activity_levels.x <- as.factor(sd_eth$activity_levels.x)

sd_eth$activity_levels.x <- relevel(sd_eth$activity_levels.x, ref = 3)   

lm_eth_vm3 <- lm(summary_count.y ~ activity_levels.x, data = sd_eth)
summary(lm_eth_vm3)



ggplot(sd_eth, aes(x = summary_count.y, y = summary_count.x, colour = activity_levels.x)) + 
        geom_point(alpha = 0.2)

```



